\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\makeatletter
\renewcommand*{\makecvtitle}{%
  \recomputecvlengths%
  \begin{minipage}[t]{\maincolumnwidth}%
    {\Huge\bfseries\color{black}\@firstname\ \@lastname}%
    \ifthenelse{\isundefined{\@title}}{}{%
      \hspace{1em}{\Large\bfseries\color{black}\@title}}%
  \end{minipage}%
  \par\vspace{1em}%
}
\makeatother\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{amssymb}
\name{Ali}{Abdallah}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \\
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \\
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}

\newcommand*{\certcventry}[5][.13em]{
  \begin{tabular*}{\maincolumnwidth}{@{}l@{\extracolsep{\fill}}r}
    \textbf{#3} & \textbf{\color{blue}\href{#2}{#4}} \\
  \end{tabular*}
  \ifx&#5&%
  \else{%
  \begin{minipage}{\maincolumnwidth}%
  \small#5%
  \end{minipage}}\fi%
  \par\addvspace{#1}}

\begin{document}

\vspace{-6mm}

\begin{center}
{\Huge\bfseries\color{black} Ali Abdallah}

\vspace{2mm}

{\Large\bfseries\color{black} RAG \& Agentic AI Engineer}

\vspace{4mm}

\begin{tabular}{ c c c }
\faMobile\enspace +201015929862 &
\faEnvelope\enspace aliabdalla2110@gmail.com &
\faGithub\enspace \color{blue}\href{https://github.com/AliAbdallah21}{GitHub} \\
\multicolumn{3}{c}{
\faLinkedin\enspace \color{blue}\href{https://www.linkedin.com/in/ali-abdallah-b5ba792b6/}{LinkedIn}
}
\end{tabular}
\end{center}

\vspace{4mm}

\section{Professional Experience}
\customcventry{06/2025 ‐ 08/2025}{{\color{blue}{Ollimi AI}}}{AI/ML Engineering Intern}{}{}{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Contributed to training and fine-tuning AI Text-to-Speech models tailored to Egyptian dialect for customer support and sales applications, improving accent accuracy by 25\%.
\item Implemented LoRA fine-tuning techniques on competing models (Coque and CSM from Unsloth AI), optimizing training pipelines and reducing inference time by 30\%.
\end{itemize}}

\customcventry{01/2025 ‐ present}{{\color{blue}{Preply}}}{AI/ML Programming Instructor}{}{}{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Taught AI/ML fundamentals, NLP, and deep learning to 50+ students, specializing in Python, TensorFlow, scikit-learn, and transformer architectures, achieving 90\% student completion rate.
\item Delivered comprehensive instruction in LLM applications, RAG systems, and vector databases, leading to 10+ successful student capstone projects.
\end{itemize}}

\section{Skills}
\begin{itemize}[label=\textbullet]
    \item \textbf{RAG \& Agentic AI:} LangChain, LlamaIndex, LangGraph, CrewAI, RAG Architectures, Multi-Agent Systems, Tool-Calling Agents, Prompt Engineering, Advanced Retrieval Strategies, Semantic Search.
    \item \textbf{AI/ML Core:} Python, TensorFlow, PyTorch, scikit-learn, Hugging Face Transformers, OpenAI API, LLM Fine-tuning, NLP, Embedding Models, Vector Search Optimization.
    \item \textbf{Data \& Deployment:} Vector Databases (ChromaDB, FAISS), PostgreSQL, MongoDB, Docker, Model Quantization, Local LLM Inference.
    \item \textbf{Development:} JavaScript, React, Node.js, Express, HTML/CSS, Git, Linux, C++, Java.
\end{itemize}

\section{Certifications}

\certcventry{https://coursera.org/verify/professional-cert/NZG474SOV13H}{IBM RAG \& Agentic AI Professional Certificate (8 Courses)}{Coursera}{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Advanced RAG architectures, LangGraph workflows, multi-agent systems with CrewAI, AutoGen, and BeeAI.
\end{itemize}}

\certcventry{https://www.coursera.org/account/accomplishments/verify/KJZRNTLVA8P2}{LangChain \& LangGraph Advanced RAG Applications}{Coursera}{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Production-ready LLM applications, advanced retrieval strategies, and stateful AI workflows.
\end{itemize}}

\certcventry{https://www.coursera.org/account/accomplishments/verify/UOWPUYUCU6D7}{Advanced LangChain, LLMOps \& Retrieval-Augmented Generation}{Coursera}{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item LLMOps pipelines, advanced RAG strategies, prompt engineering, and enterprise LLM deployment.
\end{itemize}}

\section{Education}
\customcventry{2022-2026}{\color{blue}\href{https://www.miuegypt.edu.eg/}{Misr International University}}{BSc Computer Science, AI/ML Specialization}{Cairo, Egypt}{}{}{}

\section{Projects}
{\begin{itemize}[label=\textbullet]

\item {\textbf{\href{https://github.com/AliAbdallah21/Chatterbox-Multilingual-TTS-Fine-Tuning}{Chatterbox TTS Egyptian Arabic Fine-Tuning}:} First public fine-tuning of Chatterbox Multilingual TTS for Egyptian dialect using strategic partial fine-tuning techniques. Open-source project with community adoption.}
\item {\textbf{\href{https://github.com/AliAbdallah21/Food-Recommendation-System}{Intelligent Food Recommendation System}:} RAG-powered CLI application with semantic search using ChromaDB and OpenAI embeddings, achieving 85\% recommendation accuracy with advanced filtering and conversational AI.}
\item {\textbf{\href{https://github.com/AliAbdallah21/RAG-Icebreaker-Gradio-ChatBot}{RAG Icebreaker Gradio ChatBot}:} Interactive RAG-based conversational AI using Gradio and vector similarity search with semantic retrieval pipeline, improving conversation engagement by 40\% in user testing.}

\end{itemize}}
\end{document}